%!Mode:: "TeX:UTF-8"
%!TEX encoding = UTF-8 Unicode
%!TEX TS-program = xelatex
%arara: xelatex
\documentclass{ctexart}
\newif\ifpreface
%\prefacetrue
\input{../../../global/all}
\begin{document}
\large
\setlength{\baselineskip}{1.2em}
\ifpreface
\input{../../../global/preface}
\newgeometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
\else
\newgeometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
\maketitle
\fi
%from_here_to_type
\begin{itemize}
  \item Sinologist 汉学家
  \item sonnet 十四行诗
  \item Henan is the bread basket of China.
  \item tearfully
  \item dimpled cheeks 酒窝的脸颊
  \item gleam 柔和、短暂的光
  \item short-lived=ephemeral
  \item countenance 约等于face，类似于容颜和脸。
  \item holistic 全面的
  \item holism 全面，整体
  \item get bullied/ass-kicking from sb. 被sb欺负
  \item Band-Aid solution 权宜之计
  \item Federal Express（联邦快递公司）FedEx
  \item 画龙点睛，cherry on the top: Winning the championship was great, but receiving the MVP award was the cherry on the cake.
  \item set the tone 定基调
  \item from A to Z 从头到尾
  \item the book of songs 诗经
  \item Confucian 儒家的
  \item echelon 梯队 / 阶层 / 级别
  \item paradigm 范式
  \item integrated appoarach
\end{itemize}
\section{10/10}
翻译的语法基础
\begin{itemize}
  \item 名词是单数，但是形式上是复数：crossroads
  \item 一词多义，名词单复数含义不一样：security 安全，securities 期货
  \item polysemy
  \item research on significance of leadership
\end{itemize}
翻译的知识
\begin{itemize}
  \item 杂家：jack of all trades
  \item BRI = Belt and Road Initiative
  \item 炉边谈话：fireside chat
  \item the Civil war = 美国内战 或者 英国革命 the English Revolution
  \item Emancipation Proclamation 解放黑奴宣言 增加了黑奴
  \item 富二代 silver-spoon kids
  \item status quo
  \item diamonds cut diamonds 强中自有强中手
  \item 峰会外角手段/最高级别会议 summitry
  \item 苦笑 bitter laugh
  \item 喝个痛快 drink to a thorough satisfaction
\end{itemize}

\section{10/17}
翻译的技巧
\begin{enumerate}
  \item Use as many equivalents as possible
    \begin{itemize}
      \item a sea of statistics 海量的数据
      \item UEE migrant 高考移民
      \item build suspense 制造悬念
      \item the novel is suspenseful
      \item as the name implies 顾名思义
      \item biggest holder of U.S. debt 美国最大的债权国
      \item lightning-fast 快如闪电
      \item lever woman 杠杆女（发挥自己特长帮助另一半取得事业成功的女性）
      \item useful-looking 貌似有用的
      \item a quarter-kilogram apples 半斤苹果
      \item break heart 伤心
      \item dry speech 干巴巴的演讲
      \item dry cow 一头不产奶的奶牛
      \item dry party 不喝酒的派对
      \item dry cough 干咳
      \item firewall 防火墙
      \item buffer zone 缓冲带
      \item once-triumphant superpower 曾经威风八面的超级大国
      \item plug loopholes 堵塞漏洞
      \item drunk driver 醉驾
      \item dark horse 黑马
      \item ruin health 糟蹋身体
      \item leave psychological scars 留下心灵的伤疤
      \item be on thin ice 如履薄冰
      \item quarter back 强壮 四分卫
      \item home run 取得巨大的成功
      \item marathon 持久战
      \item spring 闪电战
      \item say one thing and do another 说一套做一套
      \item twist the fact 歪曲事实
      \item thick-skinned 不知廉耻 impervious to criticism
      \item  爱面子
      \item photography almost bankrupted me. 摄影几乎让我倾家荡产
      \item preconceived judgments 先入之见
      \item over-loaded 吃饱了
      \item rob rich and help poor 劫富济贫
      \item Rob Peter to pay Paul 拆东墙补西墙
      \item rumors have legs. 以讹传讹
      \item English majors 英语专业（学生）
      \item be equally applicable to 同样适用于
      \item He is destined to have a fruitful career. 他注定会在事业方面硕果累累
      \item  Each minute of showtime requires ten years of preparation time. 台上一分钟，台下十年功。
      \item electric spark 电火花
      \item first-degree burn 一级烧伤
      \item within the allotted time 在规定时间内
      \item designated zone 在规定的地点
      \item volunteer work 志愿者工作
      \item golden age 夕阳红
      \item graduating class 毕业班
      \item graduate class 研究生班
      \item deny any Communist leanings 否认有任何共产主义倾向
      \item The earthquake flattened the whole city 地震把整个城市夷为平地
      \item return empty-handed 空手而归
      \item single-handedly 凭一己之力
      \item fiscal cliff 财政悬崖
      \item he is financially irresponsible 花钱没计划
      \item stunt show 特技表演
      \item territorial dispute 领土争端
      \item a new development paradigm with domestic circulation as the
        mainstay and domestic and international circulations reinforcing each other
        以国内大循环为主体、国内国际双循环相禒促进的新发展格局
      \item pink eye 红眼病
      \item \eng{expect nothing in return} 不求回报
      \item \eng{Iron Lady} 铁娘子
      \item \eng{sell short weight} 缺斤短两
      \item \eng{get leaked} 遭到泄露
      \item \eng{expose problem} 暴露问题
      \item \eng{supply-side structural reform} 供给侧结构性改革
      \item \eng{cement his reputation as an anthropologist} 奠定了他作为人类学家的声名
    \end{itemize}
\end{enumerate}

\section{10.24}
新闻英语
\subsection{大众性}
尼泊尔发生强震 \eng{powerful earthquake hits nepal}
\subsection{趣味性}
中国叫停葬礼上表演脱衣舞 \eng{China's funeral strippers told to cover up.}
\subsection{节俭性}
造成不孕不育的原因、不孕不育患者的治疗以及患者们的选择 \eng{Infertility: Causes, remedies and options}
\item \eng{Driving and pot: a deadly mix?} pot 是大麻的意思
The Lancet 《柳叶刀》，小而尖的外科手术刀
\item \eng{awl} 一种带尖头的小工具，用来打孔或穿洞
\item \eng{diabetes} 糖尿病
\item \eng{Silicon Valley seeks solutions for homeless} 硅谷为无家可归者寻求出路
\item \eng{Tainted rock melons recalled} 遭受污染的硬皮甜瓜被找回
\item \eng{Walmart ready to greet you this season} 沃尔玛已经做好了节日开门迎客的准备
\item \eng{}

\item \eng{watch your back!}
\end{document}
