%!Mode:: "TeX:UTF-8"
%!TEX encoding = UTF-8 Unicode
%arara: xelatex
\documentclass[12pt]{article}
\usepackage{xeCJK}
\usepackage{geometry}
\usepackage{setspace}
\geometry{a4paper, margin=1in}
\setstretch{1.4}

\begin{document}

\begin{center}
\Large \textbf{研究生学术英语翻译强化练习卷（高阶 AWL 版）} \\[0.5em]
\normalsize 共三套练习 —— 融合跨学科与高级词汇
\end{center}

\section*{第一套}

\subsection*{英译中}
\begin{enumerate}
  \item The outcomes of the study \textbf{coincide} with previous research, suggesting a universal cognitive mechanism underlying language acquisition.
  \item Any theoretical model must clearly \textbf{specify} the assumptions on which it is based.
  \item The project seeks to \textbf{allocate} resources more efficiently across departments to enhance interdisciplinary cooperation.
  \item Technological innovations often \textbf{constitute} a paradigm shift in human communication.
  \item The study revealed that external rewards may \textbf{inhibit} intrinsic motivation among participants.
\end{enumerate}

\subsection*{中译英}
\begin{enumerate}
  \item 该研究的结果与以往的实验高度一致，暗示了语言习得的普遍认知机制。  
  \item 技术创新常常构成人类交流方式的范式转变。  
  \item 研究者必须明确其理论模型所依赖的基本假设。  
  \item 外部奖励可能抑制个体的内在动机。  
  \item 本项目旨在更高效地分配各部门资源，以促进跨学科合作。
\end{enumerate}

\newpage
\section*{第二套}

\subsection*{英译中}
\begin{enumerate}
  \item The results \textbf{corroborate} the hypothesis that environmental factors significantly affect cognitive performance.
  \item The committee emphasized the need for a more \textbf{coherent} national strategy on digital education.
  \item The notion of “cultural capital” has been \textbf{invoked} to explain persistent inequalities in education.
  \item The decline in biodiversity could \textbf{trigger} irreversible ecological consequences.
  \item The policy aims to \textbf{offset} the negative impact of urban expansion through sustainable design.
\end{enumerate}

\subsection*{中译英}
\begin{enumerate}
  \item 数据进一步证实了环境因素对认知表现的显著影响。  
  \item 政府强调制定更具一致性的数字教育国家战略的必要性。  
  \item “文化资本”这一概念被用来解释教育领域中持续存在的不平等。  
  \item 生物多样性的下降可能引发不可逆转的生态后果。  
  \item 该政策旨在通过可持续设计来抵消城市扩张带来的负面影响。
\end{enumerate}

\newpage
\section*{第三套}

\subsection*{英译中}
\begin{enumerate}
  \item The proposed framework provides a \textbf{comprehensive} paradigm for analyzing discourse across disciplines.
  \item Participants were asked to evaluate various \textbf{scenarios} involving ethical decision-making.
  \item The report highlights the \textbf{predominant} role of social context in shaping individual identity.
  \item Scholars have debated whether consciousness can be \textbf{subordinated} to purely biological explanations.
  \item The forthcoming conference will \textbf{convene} leading experts to discuss advances in artificial intelligence.
\end{enumerate}

\subsection*{中译英}
\begin{enumerate}
  \item 报告强调了社会语境在塑造个体身份中的主导作用。  
  \item 研究者提出了一个用于跨学科话语分析的综合范式。  
  \item 学界一直在讨论意识是否可以完全归结为生物学层面的解释。  
  \item 即将召开的会议将汇聚人工智能领域的顶尖专家。  
  \item 参与者被要求评估涉及伦理决策的不同情境。
\end{enumerate}

\end{document}
