%!Mode:: "TeX:UTF-8"
%!TEX encoding = UTF-8 Unicode
%!TEX TS-program = xelatex
\documentclass{ctexart}
\newif\ifpreface
%\prefacetrue
\input{../../../global/all}
\begin{document}
\large
\setlength{\baselineskip}{1.2em}
\ifpreface
  \input{../../../global/preface}
\else
  %\maketitle
\fi
\newgeometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
%from_here_to_type
\begin{problem}\label{pro:4 }
  A kind of product is qualified with probability \(p(0 < p < 1)\).
  We sample these product by the following way: we check all the product at first until there appears
  \(k\) qualified product sequently. Then we check the rest of product by probability \(\alpha(0 < \alpha <1)\)
  until there appears one unqualified product, then one circle ends. Next we restart another checking
  circle. Please find out the proportion of checked product after a long time.
\end{problem}
\begin{solution}
  For sake of convenience, we call the \(k\) qualified products appearing sequently as \(k\) qualified sequence.
  Assume the proportion of checked product after a long time is \(\beta\).
  Let \(N_k\) be the amount of product when the first \(k\) qualified sequence ends. \(M_k=\mathbb{E}(N_k)\). \(G_k\) is the
  event that the next one is qualified after the first \(k-1\) qualified sequence ends. Obviously, \(\mathbb{E}(N_k-N_{k-1} \mid G_k)=1\).
  And \(\mathbb{E}(N_k-N_{k-1} \mid G_k)=\mathbb{E}(N_k) + 1\).
  Therefore, \(\mathbb{E}(N_k-N_{k-1})=p + (1-p)(\mathbb{E}(N_k) + 1)\). So \(M_{k-} M_{k-1}=p + (1-p)( 1 + M_k)\).
  Then \(pM_k=M_{k-1} + 1\). Thus, \(M_k=\frac{\frac{1}{p^k}-1}{1-p}\).
  Let \(A=\{\)The amount of product checked in one circle\(\}\), \(B=\{\)The amount of product in one circle\(\}\).
  So finding one unqualified product need average checking time \(\frac{1}{1-p}\) according to geometric distribution.
  Then we averagely need \(\frac{1}{\alpha(1-p)}\) product to find out the unqualified one.
  Then \(\mathbb{E}(A)=M_k + \frac{1}{1-p}, \mathbb{E}(B)=M_k + \frac{1}{\alpha(1-p)}\).
  So \[
    \beta = \frac{\mathbb{E}(A)}{\mathbb{E}(B)}=\frac{\frac{\frac{1}{p^k}-1}{1-p} + \frac{1}{1-p}}{\frac{\frac{1}{p^k}-1}{1-p} + \frac{1}{\alpha(1-p)}}=\frac{\alpha}{\alpha + p^k-\alpha p^k}
  \]

\end{solution}

\end{document}
